XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-25 talk/icooolps2011/paper.tex
more reference, a sentence about inlining

It has long been an objective of the partial evaluation community to
automatically produce compilers from interpreters. There has been a recent
renaissance of this idea using the different technique of tracing just-in-time
compilers. A number of projects have attempted this approach. SPUR \cite{XXX} is
a tracing JIT for .NET together with a JavaScript implementation in C\#. PyPy
\cite{armin_rigo_pypys_2006} contains a tracing JIT for RPython (a restricted
subset of Python). This JIT is then used to trace a number of languages
implementations written in RPython. A number of other experiments in this
directions were done, such as an interpreter for Lua in JavaScript, which is run
on and optimized with a tracing JIT for JavaScript
\cite{yermolovich_optimization_2009}.

@@

A recently popular approach to JIT compilers is that of tracing JITs. Tracing
JITs have their origin in the Dynamo project which used the for dynamic
assembler optimization \cite{XXX}. Later they were used for to implement
a lightweight JIT for Java \cite{XXX} and for dynamic languages such as
JavaScript \cite{XXX}.

A tracing JIT works by recording traces of concrete execution paths through the
program. Those
traces are therefore linear list of operations, which are optimized and then
get turned into machine code. To be able to do this recording, VMs with a
tracing JIT typically contain an interpreter. After a user program is
started the interpreter is used until the most important paths through the user
program are turned into machine code. The tracing JIT tries to produce traces
that correspond to loops in the traced program, but most tracing JITs now also
have support for tracing non-loops \cite{XXX}.

>>>>

It has long been an objective of the partial evaluation community to
automatically produce compilers from interpreters. There has been a recent
renaissance of this idea using the different technique of tracing just-in-time
compilers. A number of projects have attempted this approach. SPUR \cite{bebenita_spur:_2010} is
a tracing JIT for .NET together with a JavaScript implementation in C\#. PyPy
\cite{armin_rigo_pypys_2006} contains a tracing JIT for RPython (a restricted
subset of Python). This JIT is then used to trace a number of languages
implementations written in RPython. A number of other experiments in this
directions were done, such as an interpreter for Lua in JavaScript, which is run
on and optimized with a tracing JIT for JavaScript
\cite{yermolovich_optimization_2009}.

@@

A recently popular approach to JIT compilers is that of tracing JITs. Tracing
JITs have their origin in the Dynamo project which used the for dynamic
assembler optimization \cite{bala_dynamo:_2000}. Later they were used for to implement
a lightweight JIT for Java \cite{gal_hotpathvm:_2006} and for dynamic languages such as
JavaScript \cite{gal_trace-based_2009}.

A tracing JIT works by recording traces of concrete execution paths through the
program. Those
traces are therefore linear list of operations, which are optimized and then
get turned into machine code. This recording automatically inlines functions,
when a function call is encountered the operations of the called functions are
simply put into the trace too.

To be able to do this recording, VMs with a
tracing JIT typically contain an interpreter. After a user program is
started the interpreter is used until the most important paths through the user
program are turned into machine code. The tracing JIT tries to produce traces
that correspond to loops in the traced program, but most tracing JITs now also
have support for tracing non-loops \cite{XXX}.
